Automatic detection of bad habits of programming in Scratch

### 2014-04-15 paperFIE_en.tex
Fix errata

\section{Introduction}
Scratch \cite{resnick2009scratch}  is a programming environment that includes a visual programming language designed for children from 6 years old, a development environment and a website where the community can host their projects; run, study and reuse other programs; and share ideas or suggestions with other programmers. Although there are several similar visual programming languages​​, Scratch is undoubtedly the most successful and the one that is being used more regularly worldwide, with more than three million registered users on its website and more than five million shared project in its repository \footnote{http://scratch.mit.edu/statistics/}.
\paragraph{}Scratch is being used both in extracurricular activities \cite{maloney2008programming, kafai2010entering} or summer camps \cite{adams2010scratching, franklin2013assessment}, as in schools \cite{wilson2012evaluation}, high schools \cite{meerbaum2013learning} and even universities worldwide \cite{wolz2009starting, malan2007scratch}. Its capacity to bring computer programming to children and youth with the aim that in the future they would be willing to continue their studies in this discipline, and also its success to teach both basic and advanced programming concepts has been documented.
\paragraph{}However, it is also possible to find studies that have detected some bad programming habits in students learning to program in this environment \cite{meerbaum2011habits}. In this line, in our work as teachers we have detected other bad habits that, despite insisting our students to try to avoid them, we see how they are constantly repeated by pupils learning to program in Scratch. As these habits are contrary to the basic programming recommendations, our study tries to detect if they are also common in the projects shared on the Scratch repository and propose some ideas to try to avoid such situations.
\paragraph{}In section 2 a brief overview of Scratch is presented, works that study the learning demonstrated by students learning to program in this environment are reviewed, and studies that automate the evaluation of this learning are exposed. In section 3, our work methodology is described. Section 4 presents the obtained results. Finally, in section 5 the conclusions of our study are discussed and some ideas and suggestions for future work are provided.

>>>>

\section{Introduction}
Scratch \cite{resnick2009scratch}  is a programming environment that includes a visual programming language designed for children from 6 years old, a development environment and a website where the community can host their projects; run, study and reuse other programs; and share ideas or suggestions with other programmers. Although there are several similar visual programming languages, Scratch is undoubtedly the most successful and the one that is being used more regularly worldwide, with more than three million registered users on its website and more than five million shared project in its repository \footnote{http://scratch.mit.edu/statistics/}.
\paragraph{}Scratch is being used both in extracurricular activities \cite{maloney2008programming, kafai2010entering} or summer camps \cite{adams2010scratching, franklin2013assessment}, as in schools \cite{wilson2012evaluation}, high schools \cite{meerbaum2013learning} and even universities worldwide \cite{wolz2009starting, malan2007scratch}. Its capacity to bring computer programming to children and youth with the aim that in the future they would be willing to continue their studies in this discipline, and also its success to teach both basic and advanced programming concepts has been documented.
\paragraph{}However, it is also possible to find studies that have detected some bad programming habits in students learning to program in this environment \cite{meerbaum2011habits}. In this line, in our work as teachers we have detected other bad habits that, despite insisting our students to try to avoid them, we see how they are constantly repeated by pupils learning to program in Scratch. As these habits are contrary to the basic programming recommendations, our study tries to detect if they are also common in the projects shared on the Scratch repository and propose some ideas to try to avoid such situations.
\paragraph{}In section 2 a brief overview of Scratch is presented, works that study the learning demonstrated by students learning to program in this environment are reviewed, and studies that automate the evaluation of this learning are exposed. In section 3, our work methodology is described. Section 4 presents the obtained results. Finally, in section 5 the conclusions of our study are discussed and some ideas and suggestions for future work are provided.
